Title

### 2017-05-09 paper/paper.tex

>>>>

The \texttt{Ridge Fair algorithm} was also implemented as presented in (Joseph et al., 2016). This algorithm is very similar in implementation to Interval Chaining, save that it’s narrower confidence intervals allow for derivation of tighter regret bounds. Some details to note are that we assume for simplicity (and without loss of generality) that our parameter R = 1 and that we play uniformly randomly among all arms.
